Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline

### 2014-01-13 paper.tex
Enumerated tasks and updated note on reviewer 1

{\color{blue}
I am not very enthusiastic about his paper as it does not contain many novel or original ideas and finding. On the electrochemistry side it is superficial and falls back behind published state of the art and textbook knowledge.\\
{\color{OliveGreen}
    {\color{Red} Research textbook knowledge and published state of the art relating to electro chemistry in our area.}
    No response yet.
}\\

1. The interface model as such is not new and has been published extensively.\\
{\color{OliveGreen} 
    {\color{Red} Review and discuss existing interface models}
    No response yet.
}\\

2. The authors do not at all comment on interface polarization, which is particularly important under DC conditions. As soon as an electrode carries current, such phenomena become important and relevant.\\
{\color{OliveGreen}
    {\color{Red} Is polarisation a separate mechanism from double layer formation? If so, can we address? Polarisation will be just as important in cyclic measurement techniques where the cycle time is low. Does anyone understand polarisation sufficiently to remove it from measurements? Is polarisation not just remaining charge in a layer around an electrode, is it not just the double layer?}
    No response yet.
}\\

3. To assess the resistivity or impedance of a material between two electrodes, one normally uses a 4-electrode setup with injection of current through the two outer electrodes, while measuring a voltage between the inner ones. This is particularly relevant for the measurements in Fig. 3 and the related and subsequent text.\\
{\color{OliveGreen} 
    {\color{Red} I don't understand what use doing this would be. All voltage dropped between two end electrodes, voltage proportional to total impedance between electrodes. The most use you could get from this would be to find how much is dropped across a single interface, which is exactly what we are doing.}
    No response yet.    
}\\

4. The authors never mention the origin of any Faradaic contribution at the electrodes. What is the electro- or redox-chemistry that the authors assume to happen?? Gas formation at the electrodes, electrolysis of the saline, i.e., hydrogen and oxygen formation??\\
{\color{OliveGreen}
    {\color{Red} My assumption is that we don't give a crap what it is, whatever it is, we're modelling it. If you want to know that, look elsewhere.}
    No response yet.
}\\

5. Figure 5 is not referenced anywhere in the text. Also the blue variations in the curves are hardly visible.\\
{\color{OliveGreen} 
    {\color{Red} Enhance color variation in Figures 4 and 5 and make a reference to Figure 5}
    No response yet.
}\\

6. Since the electrode model includes two back-to-back diodes, I think it would be valuable to sweep the voltage from -1.2V to +1.2V.\\
{\color{OliveGreen}
    {\color{Red} The diodes are identical, this is moving into polarisation territory again. In effect, they are both being used (one by + and other by -). I don't know what to say about this. We wanted to make all the measurements happen in as little time as possible. We have data from sweeps in the other direction, not DC though.}
    No response yet.
}\\

7. There is a big difference between blue dots and red curve in Fig. 10, except for the "voltage increment time" and "64 seconds after increment".  This indicates to me that the CPE model is NOT that accurate, as the settling curve is highly correlated to the CPE parameters.\\
{\color{OliveGreen}
    {\color{Red} This is true, try and pinpoint exactly why this is happening. Why does the CPE perform so well in the CPE frequency response plots yet so poorly in the Faradaic part?}
    No response yet.
}\\
}

@@

page 2, in text/ table II. The scaling parameters and their meanings should be described more comprehensively. They remain somewhat unclear and meaningless to reader.\\
{\color{OliveGreen}
    {\color{Red} Pull in more explination from JonathanScott2013 relating to the resistor mesh}
    No response yet.
}\\

page 2 Measurement of the CPE. What was the current density used in EIS measurements?
What is the effect of chosen current density on CPE impedance (Fig. 5)?
{\color{OliveGreen}
    {\color{Red} Estimate current density and investigate possible effects}
    No response yet.
}

In addition,  measurement apparatus information is fully lacking.\\
{\color{OliveGreen}
    {\color{Red} Describe instruments used in measurements or make reference to Jonathans paper}
    No response yet.
}\\

page 2, line 52. "the magnitude shifts relatively little". However, In Fig. 4, logaritmic scale is used, and the change from 1.0X to 0.025X is almost 50k at the lowest frequencies. 
please clarify this point.\\
{\color{OliveGreen}
    {\color{Red} ``shifts relatively little'' meaning at this impedance 50k is small compared to total resistance''}
    No response yet.
}\\

page 3, in text/ table III. The parameters (m, k..) and their meanings should be described more comprehensively, as well.\\
{\color{OliveGreen} 
    {\color{Red} Describe the parameters m and k in the resistor network (pull from Jonathans paper and sub-references)}
    No response yet.
}\\

Figure 9 (page 4). There is a clear difference in behavior of faradic conduction between 0.25X (red curve) and 0.5X (green curve). Transient current occur at 0.95V (<0.25X PBS) changing to occur at 1.0 V (>0.5X PBS). This behavior has not discussed in manuscript at all. Please revise it.\\
{\color{OliveGreen}
    {\color{Red} Should be easy to do, perhaps I make a second graph that shows more of the time data}
    No response yet.
}\\

page 4. Referencing (in the text) to the Fig. 10 is lacking (?).\\
{\color{OliveGreen}
    {\color{Red} Include a reference to Figure 10 in the document}
    No response yet.
}\\

Finally, and most importantly, the part of in vivo measurements are very limited since only one spinal channel measurement has been performed. My opinion is that this manuscript could be even better without this uncertain (n=1) result and thus I recommend to leave this part out.\\
{\color{OliveGreen}
    {\color{Red} Leave sheep in but perhaps show the second measurement (day 1) if possible (4th reviewer found sheep correlation to PBS result interesting). Would a separate sheep measurement graph be of use showing all sheep results? Or do we hold onto this for the better phantom paper?}
    No response yet.
}\\
}

@@

{\color{blue}
Authors
The aim of this paper, to find a SPICE model of implanted electrodes, is important and the results presented in the paper are interesting. However, as it stands the paper is not well written and must be revised. The weaknesses of the paper are an unclear structure, with results and discussion mixed, poor attention to detail and inaccurate use of words.\\
{\color{OliveGreen}
    {\color{Red} Revise poor use of words (perhaps relating to model elements/physical elements). Perhaps separate the results and discussion sections.} 
    No response yet.
}\\

@@

1. You do not explain how the impedance measurements have been made (Figs 4, 5 13 & 14). I want to know how much charge was being applied to these electrodes at low frequencies (e.g. 0.05 Hz): what potential excursion occurred was it really a ``small signal''?\\
{\color{OliveGreen}
    {\color{Red} Estimate the amount of charge being injected in each of the measurements (fits with the current density)}
    No response yet.
}\\

2. I think that the classical view of the electrochemistry of Pt in saline (as, for example, expressed in your ref 1), is that the electrolysis reactions (oxygen and hydrogen evolution) start with a potential difference of about 1.4V. Below this p.d., the likeliest reaction is reduction of oxygen at the cathode which could accompany oxygen evolution from water at the anode. Your paper lacks any consideration of the chemistry but this is a important fault in the stepped-current experiment. Was the solution in equilibrium with air before the experiment? If this is a model for electrodes in vivo, should not the PBS have been in equilibrium with gas with the in vivo partial pressure of oxygen? I suggest that you repeat this experiment, at least (i) under air, (ii) under nitrogen, & perhaps (iii) under in vivo partial pressure of oxygen. The stirring arrangements ought to be exactly described too because liquid flow may be critical.\\
{\color{OliveGreen}
    {\color{Red} This represents a lot of work to redo the measurements. Perhaps we make it clear that we don't know the electrochemistry side, that it's simply out of our depth, and any hypothesis we draw based on electrochemistry may harm the validity of our work. If we explain more exactly the proceedure we took so as to be more repeatable and hint that we're not interested at this point on the electrochemistry, that we only wish to make the model behave like the solution.}
    No response yet.
}

@@

1. P1, top RH col. ``0.1X'' ought to be explained when you first use this form.\\
{\color{OliveGreen}
    {\color{Red} Replace ``A 0.1X concentration'' with ``a one-tenth concentration...'' and explain exactly what that means.}
    No response yet.
}\\

2. Should the resistor model of the volume conductor from [4] be shown in this paper? It would make the paper easier to understand for your reader if you showed the model. If you are not going to do so, you might help them by saying something like ``Readers are advised to see [4] to understand the meaning of the parameters in Table II''.\\
{\color{OliveGreen}
    {\color{Red} Leave until the end, if we have the space then we put it in, otherwise put a better reference to ScottSingle2013}
    No response yet.
}\\

3. You say (p2 line 43) that there are 2 independent scaling factors. Is Rli independent or not? If not, why input it in Table II?\\
{\color{OliveGreen}
    {\color{Red} Mention that $R_{li}$ is not independent because of the geometric simplification of the resistor network. Mention that for more detail we suggest viewers read the relevant section of ScottSingle2013}
    No response yet.
}\\

4. In the legend of Fig 4 and in paragraph below, you say this is magnitude of the CPE. But surely it is not since the sloping lines become horizontal. It is the CPE in series with something. But what is this something? Is it the total series resistance or have you already subtracted the volume resistance (found in section II)?\\
{\color{OliveGreen}
    {\color{Red} Reword the caption of Fig. 4 to include the series resistance.}
    No response yet.
}\\

5. The previous point is complicated by your statement that Rs (Fig 2) is an addition to the volume resistance (p2 RH col). Why is Rs necessary? Is it because the resistance values at high frequencies in Fig 4 are not consistent with the values from the resistor network found in section II? If so, this would be very interesting and I would like you to bring this out.\\
{\color{OliveGreen} 
    {\color{Red} His reasoning is correct, it is because the impedance does not match at high freq. I had the graph with dotted lines to show the difference that Rs made. Jonathan, you thought this was too messy and it was removed, should it be added back in again?}
    No response yet.
}\\

6. P2, col 2, line 24: why 2 & 7?\\
{\color{OliveGreen}
    {\color{Red} Explain more clearly why electrodes 2 and 7 were chosen (to avoid end effects)}
    No response yet.
}\\

7. P2, col 2, line 53: ``implying that its behaviour is a property of Pt and water''. Previous authors have thought this showed that the CPE depended on the geometry (surface roughness) of the electrode. Did you mean that, or were you thinking of the electrochemical properties of Pt. Please make clearer.\\
{\color{OliveGreen}
    {\color{Red} We aren't sure of either but further work into the surface area of the electrode via ottonisation should reveal whether surface area is a factor - read: followup publication}
    No response yet.
}\\

8. You do not explain why, in eq 1, you want to use this form. Why nVt? I suppose it isso you can use a standard SPICE form rather than this suits the data. Is that right?\\
{\color{OliveGreen} 
    {\color{Red} Investigate other forms, comment on why this has been chosen}
    No response yet.
}\\

9. P3, col 2, line 31: why 2 and 6?\\
{\color{OliveGreen}
    {\color{Red} Took resistance measurements of lead and electrode 2 is open circuit inside the electrode. Must have meant 3 and 7, due to damaged electrode 2}
    No response yet.
}\\

10. P3, col 2, line 36. I guess you mean what is usually called a Magnetic Stirrer. Not ``inductive'' surely?\\
{\color{OliveGreen} 
    {\color{Red} What I originally thought, I don't know where inductive stirrer came from}
    No response yet.
}\\

11. P3 footnote. ``The response of the CPE'': this is confusing! Surely this is the response of a pair of electrodes? The CPE is an element of your model.\\
{\color{OliveGreen} 
    {\color{Red} This must form part of the inaccurate use of words comment. It's not right to say response of a pair of electrodes since there are other effects. Reword.}
    No response yet.
}\\

12. Fig 11 legend ``Simulated and measured response of the interface model''. Surely you mean ``Simulated response of the interface model compared to measurement from the electrodes''?\\
{\color{OliveGreen}
    {\color{Red} Yes, this is better. Replace with this.}
    No response yet.
}\\

13. P5, col 2, line 46 ``the CPE is setting''. Again, you are confusing an element of your model with reality.\\
{\color{OliveGreen}
    {\color{Red} Correct, maybe a diargam of the hypothesis is required - nobody seemed to dispute the hypothesis. Check there is no ``textbook knowledge'' explanation for this beforehand.}
    No response yet.
}\\

14. P5, col 1, line 49 ``a 0.25X PBS is a good model''.  This seems a very feeble comment on an interesting result. The series resistance part of the in vivo magnitude is a good fit to the 0.25X curve and the slope of the CPS is very similar (though you have exaggerated this by extrapolating nearly 2 decades in frequency below the lowest-frequency measurement). But the impedance at low frequencies is about three times too high. How do you explain that? It cannot be because of the bone and other high-resistivity structures around the electrodes (which would have an effect on the high frequency asymptote). So what is it? Did you measure the electrodes again in PBS after removing from the sheep? Troyk published an interesting paper with measurement from electrodes in brain of zebra finches which showed that anomalous characteristics in vivo vanished as soon as the electrodes were returned to PBS, implying that the phenomenon was not due to some biofilm deposited on the electrodes.\\
{\color{OliveGreen}
    {\color{Red} True, a feeble comment on PBS match. It may be worth noting the phase of measured data in sheep indicating that the sheep itself was reactive. There may be data at those lower points (to justify extrapolating), check. Have we measured the electrodes again since inserting into the sheep, I think we have but check.  Read the paper by Troyk, comment on applicability. Maybe there is test data between sheep in saline showing the electrodes returning to normal, check.}.
    No response yet.
}\\
}

@@

Overall, the paper was brief and to the point, which in this case is actually a determent instead of a benefit. Much of the underlying theory and development of parameters appear without informing the reader of their purpose or how they were calculated and/or measured. 
For example, the parameters in Table 2 (and reported to be in Figure 3) are not explained and what their relationship to the remainder of the manuscript is not provided. 
{\color{OliveGreen}
    {\color{Red} Explain parameters in table two better or refer readers to ScottSingle2013}
    No response yet.
}
To make this manuscript more approachable to a wider audience, I recommend the authors more fully develop Sections II, III, and IV. Further, they should explain their testing in terms of standard electrochemical characterization, detailing their counter, working, and reference electrodes used in measuring impedance. 
{\color{OliveGreen}
    {\color{Red} Try to include any relevant electrochemical information, find out what that is first}
    No response yet.
}
As part of this expansion, the references should be increased beyond the present ten references. Although their current references include clearly important electrode characterization references (Cogan, Merrill et. al, & Kane et. al), the information contained in these references are not effectively used to support the authors’ work.\\
{\color{OliveGreen}
    {\color{Red} Perhaps Troyk could be added. A search for textbook knowledge and more published state of the art should uncover more references}
    No response yet.
}\\

Technically, I found one issue with this paper. In Figure 11, the x-axis labels should have 2 digits after the decimal. As presently shown, each of the labels 0.6, 0.7, ..., 1.0 are repeated twice on the axis. Presumably, the second version of the labels should be 0.65, 0.75, ..., 1.05.\\
{\color{OliveGreen}
    {\color{Red} Definitely, how did I miss that?}
    No response yet.
}\\
}
\end{document}

>>>>

{\color{blue}
I am not very enthusiastic about his paper as it does not contain many novel or original ideas and finding. On the electrochemistry side it is superficial and falls back behind published state of the art and textbook knowledge.\\
{\color{OliveGreen}
    Item 1\\
    {\color{Red} Research textbook knowledge and published state of the art relating to electro chemistry in our area.}
    No response yet.
}\\

1. The interface model as such is not new and has been published extensively.\\
{\color{OliveGreen}
    Item 2\\
    {\color{Red} Review and discuss existing interface models}
    No response yet.
}\\

2. The authors do not at all comment on interface polarization, which is particularly important under DC conditions. As soon as an electrode carries current, such phenomena become important and relevant.\\
{\color{OliveGreen}
    Item 3\\
    {\color{Red} Is polarisation a separate mechanism from double layer formation? If so, can we address? Polarisation will be just as important in cyclic measurement techniques where the cycle time is low. Does anyone understand polarisation sufficiently to remove it from measurements? Is polarisation not just remaining charge in a layer around an electrode, is it not just the double layer?}
    No response yet.
}\\

3. To assess the resistivity or impedance of a material between two electrodes, one normally uses a 4-electrode setup with injection of current through the two outer electrodes, while measuring a voltage between the inner ones. This is particularly relevant for the measurements in Fig. 3 and the related and subsequent text.\\
{\color{OliveGreen} 
    Item 4\\
    {\color{Red} I don't understand what use doing this would be. All voltage dropped between two end electrodes, voltage proportional to total impedance between electrodes. The most use you could get from this would be to find how much is dropped across a single interface, which is exactly what we are doing.}
    No response yet.    
}\\

4. The authors never mention the origin of any Faradaic contribution at the electrodes. What is the electro- or redox-chemistry that the authors assume to happen?? Gas formation at the electrodes, electrolysis of the saline, i.e., hydrogen and oxygen formation??\\
{\color{OliveGreen}
    Item 5\\
    {\color{Red} Do we wish to get into this? Perhaps we could touch on it (after reviewing electrochemistry literature) but leave it loose and mention that it is not our intention to completely understand the mechanisims at the chemical level, rather to compare an available model with measurements and comment.}
    No response yet.
}\\

5. Figure 5 is not referenced anywhere in the text. Also the blue variations in the curves are hardly visible.\\
{\color{OliveGreen} 
    Item 6\\
    {\color{Red} Enhance color variation in Figures 4 and 5 and make a reference to Figure 5}
    No response yet.
}\\

6. Since the electrode model includes two back-to-back diodes, I think it would be valuable to sweep the voltage from -1.2V to +1.2V.\\
{\color{OliveGreen}
    Item 7\\
    {\color{Red} The diodes are identical, this is moving into polarisation territory again. In effect, they are both being used (one by + and other by -). I don't know what to say about this. We wanted to make all the measurements happen in as little time as possible. We have data from sweeps in the other direction, not DC though.}
    No response yet.
}\\

7. There is a big difference between blue dots and red curve in Fig. 10, except for the "voltage increment time" and "64 seconds after increment".  This indicates to me that the CPE model is NOT that accurate, as the settling curve is highly correlated to the CPE parameters.\\
{\color{OliveGreen}
    Item 8\\
    {\color{Red} This is true, try and pinpoint exactly why this is happening. Why does the CPE perform so well in the CPE frequency response plots yet so poorly in the Faradaic part?}
    No response yet.
}\\
}

@@

page 2, in text/ table II. The scaling parameters and their meanings should be described more comprehensively. They remain somewhat unclear and meaningless to reader.\\
{\color{OliveGreen}
    Item 9\\
    {\color{Red} Pull in more explination from JonathanScott2013 relating to the resistor mesh}
    No response yet.
}\\

page 2 Measurement of the CPE. What was the current density used in EIS measurements?
What is the effect of chosen current density on CPE impedance (Fig. 5)?
{\color{OliveGreen}
    Item 10\\
    {\color{Red} Estimate current density and investigate possible effects}
    No response yet.
}

In addition,  measurement apparatus information is fully lacking.\\
{\color{OliveGreen}
    Item 11\\
    {\color{Red} Describe instruments used in measurements or make reference to Jonathans paper}
    No response yet.
}\\

page 2, line 52. "the magnitude shifts relatively little". However, In Fig. 4, logaritmic scale is used, and the change from 1.0X to 0.025X is almost 50k at the lowest frequencies. 
please clarify this point.\\
{\color{OliveGreen}
    Item 12\\
    {\color{Red} ``shifts relatively little'' meaning at this impedance 50k is small compared to total resistance''}
    No response yet.
}\\

page 3, in text/ table III. The parameters (m, k..) and their meanings should be described more comprehensively, as well.\\
{\color{OliveGreen} 
    Item 13\\
    {\color{Red} Describe the parameters m and k in the resistor network (pull from Jonathans paper and sub-references)}
    No response yet.
}\\

Figure 9 (page 4). There is a clear difference in behavior of faradic conduction between 0.25X (red curve) and 0.5X (green curve). Transient current occur at 0.95V (<0.25X PBS) changing to occur at 1.0 V (>0.5X PBS). This behavior has not discussed in manuscript at all. Please revise it.\\
{\color{OliveGreen}
    Item 14\\
    {\color{Red} Should be easy to do, perhaps I make a second graph that shows more of the time data}
    No response yet.
}\\

page 4. Referencing (in the text) to the Fig. 10 is lacking (?).\\
{\color{OliveGreen}
    Item 15\\
    {\color{Red} Include a reference to Figure 10 in the document}
    No response yet.
}\\

Finally, and most importantly, the part of in vivo measurements are very limited since only one spinal channel measurement has been performed. My opinion is that this manuscript could be even better without this uncertain (n=1) result and thus I recommend to leave this part out.\\
{\color{OliveGreen}
    Item 16\\ 
    {\color{Red} Leave sheep in but perhaps show the second measurement (day 1) if possible (4th reviewer found sheep correlation to PBS result interesting). Would a separate sheep measurement graph be of use showing all sheep results? Or do we hold onto this for the better phantom paper?}
    No response yet.
}\\
}

@@

{\color{blue}
Authors
The aim of this paper, to find a SPICE model of implanted electrodes, is important and the results presented in the paper are interesting. However, as it stands the paper is not well written and must be revised. The weaknesses of the paper are an unclear structure, with results and discussion mixed, poor attention to detail and inaccurate use of words.\\
{\color{OliveGreen}
    Item 17\\
    {\color{Red} Revise poor use of words (perhaps relating to model elements/physical elements). Perhaps separate the results and discussion sections.} 
    No response yet.
}\\

@@

1. You do not explain how the impedance measurements have been made (Figs 4, 5 13 & 14). I want to know how much charge was being applied to these electrodes at low frequencies (e.g. 0.05 Hz): what potential excursion occurred was it really a ``small signal''?\\
{\color{OliveGreen}
    Item 18\\
    {\color{Red} Estimate the amount of charge being injected in each of the measurements (fits with the current density)}
    No response yet.
}\\

2. I think that the classical view of the electrochemistry of Pt in saline (as, for example, expressed in your ref 1), is that the electrolysis reactions (oxygen and hydrogen evolution) start with a potential difference of about 1.4V. Below this p.d., the likeliest reaction is reduction of oxygen at the cathode which could accompany oxygen evolution from water at the anode. Your paper lacks any consideration of the chemistry but this is a important fault in the stepped-current experiment. Was the solution in equilibrium with air before the experiment? If this is a model for electrodes in vivo, should not the PBS have been in equilibrium with gas with the in vivo partial pressure of oxygen? I suggest that you repeat this experiment, at least (i) under air, (ii) under nitrogen, & perhaps (iii) under in vivo partial pressure of oxygen. The stirring arrangements ought to be exactly described too because liquid flow may be critical.\\
{\color{OliveGreen}
    Item 19\\
    {\color{Red} This represents a lot of work to redo the measurements. Perhaps we make it clear that we don't know the electrochemistry side, that it's simply out of our depth, and any hypothesis we draw based on electrochemistry may harm the validity of our work. If we explain more exactly the proceedure we took so as to be more repeatable and hint that we're not interested at this point on the electrochemistry, that we only wish to make the model behave like the solution.}
    No response yet.
}

@@

1. P1, top RH col. ``0.1X'' ought to be explained when you first use this form.\\
{\color{OliveGreen}
    Item 20\\
    {\color{Red} Replace ``A 0.1X concentration'' with ``a one-tenth concentration...'' and explain exactly what that means.}
    No response yet.
}\\

2. Should the resistor model of the volume conductor from [4] be shown in this paper? It would make the paper easier to understand for your reader if you showed the model. If you are not going to do so, you might help them by saying something like ``Readers are advised to see [4] to understand the meaning of the parameters in Table II''.\\
{\color{OliveGreen}
    Item 21\\
    {\color{Red} Leave until the end, if we have the space then we put it in, otherwise put a better reference to ScottSingle2013}
    No response yet.
}\\

3. You say (p2 line 43) that there are 2 independent scaling factors. Is Rli independent or not? If not, why input it in Table II?\\
{\color{OliveGreen}
    Item 22\\
    {\color{Red} Mention that $R_{li}$ is not independent because of the geometric simplification of the resistor network. Mention that for more detail we suggest viewers read the relevant section of ScottSingle2013}
    No response yet.
}\\

4. In the legend of Fig 4 and in paragraph below, you say this is magnitude of the CPE. But surely it is not since the sloping lines become horizontal. It is the CPE in series with something. But what is this something? Is it the total series resistance or have you already subtracted the volume resistance (found in section II)?\\
{\color{OliveGreen}
    Item 23\\
    {\color{Red} Reword the caption of Fig. 4 to include the series resistance.}
    No response yet.
}\\

5. The previous point is complicated by your statement that Rs (Fig 2) is an addition to the volume resistance (p2 RH col). Why is Rs necessary? Is it because the resistance values at high frequencies in Fig 4 are not consistent with the values from the resistor network found in section II? If so, this would be very interesting and I would like you to bring this out.\\
{\color{OliveGreen} 
    Item 24\\
    {\color{Red} His reasoning is correct, it is because the impedance does not match at high freq. I had the graph with dotted lines to show the difference that Rs made. Jonathan, you thought this was too messy and it was removed, should it be added back in again?}
    No response yet.
}\\

6. P2, col 2, line 24: why 2 & 7?\\
{\color{OliveGreen}
    Item 25\\
    {\color{Red} Explain more clearly why electrodes 2 and 7 were chosen (to avoid end effects)}
    No response yet.
}\\

7. P2, col 2, line 53: ``implying that its behaviour is a property of Pt and water''. Previous authors have thought this showed that the CPE depended on the geometry (surface roughness) of the electrode. Did you mean that, or were you thinking of the electrochemical properties of Pt. Please make clearer.\\
{\color{OliveGreen}
    Item 26\\
    {\color{Red} We aren't sure of either but further work into the surface area of the electrode via ottonisation should reveal whether surface area is a factor - read: followup publication}
    No response yet.
}\\

8. You do not explain why, in eq 1, you want to use this form. Why nVt? I suppose it isso you can use a standard SPICE form rather than this suits the data. Is that right?\\
{\color{OliveGreen} 
    Item 27\\
    {\color{Red} Investigate other forms, comment on why this has been chosen}
    No response yet.
}\\

9. P3, col 2, line 31: why 2 and 6?\\
{\color{OliveGreen}
    Item 28\\
    {\color{Red} Took resistance measurements of lead and electrode 2 is open circuit inside the electrode. Must have meant 3 and 7, due to damaged electrode 2}
    No response yet.
}\\

10. P3, col 2, line 36. I guess you mean what is usually called a Magnetic Stirrer. Not ``inductive'' surely?\\
{\color{OliveGreen} 
    Item 29\\
    {\color{Red} What I originally thought, I don't know where inductive stirrer came from}
    No response yet.
}\\

11. P3 footnote. ``The response of the CPE'': this is confusing! Surely this is the response of a pair of electrodes? The CPE is an element of your model.\\
{\color{OliveGreen} 
    Item 30\\
    {\color{Red} This must form part of the inaccurate use of words comment. It's not right to say response of a pair of electrodes since there are other effects. Reword.}
    No response yet.
}\\

12. Fig 11 legend ``Simulated and measured response of the interface model''. Surely you mean ``Simulated response of the interface model compared to measurement from the electrodes''?\\
{\color{OliveGreen}
    Item 31\\
    {\color{Red} Yes, this is better. Replace with this.}
    No response yet.
}\\

13. P5, col 2, line 46 ``the CPE is setting''. Again, you are confusing an element of your model with reality.\\
{\color{OliveGreen}
    Item 32\\
    {\color{Red} Correct, maybe a diargam of the hypothesis is required - nobody seemed to dispute the hypothesis. Check there is no ``textbook knowledge'' explanation for this beforehand.}
    No response yet.
}\\

14. P5, col 1, line 49 ``a 0.25X PBS is a good model''.  This seems a very feeble comment on an interesting result. The series resistance part of the in vivo magnitude is a good fit to the 0.25X curve and the slope of the CPS is very similar (though you have exaggerated this by extrapolating nearly 2 decades in frequency below the lowest-frequency measurement). But the impedance at low frequencies is about three times too high. How do you explain that? It cannot be because of the bone and other high-resistivity structures around the electrodes (which would have an effect on the high frequency asymptote). So what is it? Did you measure the electrodes again in PBS after removing from the sheep? Troyk published an interesting paper with measurement from electrodes in brain of zebra finches which showed that anomalous characteristics in vivo vanished as soon as the electrodes were returned to PBS, implying that the phenomenon was not due to some biofilm deposited on the electrodes.\\
{\color{OliveGreen}
    Item 33\\
    {\color{Red} True, a feeble comment on PBS match. It may be worth noting the phase of measured data in sheep indicating that the sheep itself was reactive. There may be data at those lower points (to justify extrapolating), check. Have we measured the electrodes again since inserting into the sheep, I think we have but check.  Read the paper by Troyk, comment on applicability. Maybe there is test data between sheep in saline showing the electrodes returning to normal, check.}.
    No response yet.
}\\
}

@@

Overall, the paper was brief and to the point, which in this case is actually a determent instead of a benefit. Much of the underlying theory and development of parameters appear without informing the reader of their purpose or how they were calculated and/or measured. 
For example, the parameters in Table 2 (and reported to be in Figure 3) are not explained and what their relationship to the remainder of the manuscript is not provided. 
{\color{OliveGreen}
    Item 34\\
    {\color{Red} Explain parameters in table two better or refer readers to ScottSingle2013}
    No response yet.
}
To make this manuscript more approachable to a wider audience, I recommend the authors more fully develop Sections II, III, and IV. Further, they should explain their testing in terms of standard electrochemical characterization, detailing their counter, working, and reference electrodes used in measuring impedance. 
{\color{OliveGreen}
    Item 35\\
    {\color{Red} Try to include any relevant electrochemical information, find out what that is first}
    No response yet.
}
As part of this expansion, the references should be increased beyond the present ten references. Although their current references include clearly important electrode characterization references (Cogan, Merrill et. al, & Kane et. al), the information contained in these references are not effectively used to support the authors’ work.\\
{\color{OliveGreen}
    Item 36\\
    {\color{Red} Perhaps Troyk could be added. A search for textbook knowledge and more published state of the art should uncover more references}
    No response yet.
}\\

Technically, I found one issue with this paper. In Figure 11, the x-axis labels should have 2 digits after the decimal. As presently shown, each of the labels 0.6, 0.7, ..., 1.0 are repeated twice on the axis. Presumably, the second version of the labels should be 0.65, 0.75, ..., 1.05.\\
{\color{OliveGreen}
    Item 37\\
    {\color{Red} Definitely, how did I miss that?}
    No response yet.
}\\
}
\end{document}
